Data Preparation

### 2019-01-10 Data Preparation.Rmd

### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.

@@

```{r import d_transcript}
d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                     read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
  distinct()
```

>>>>

### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.

@@

```{r import d_transcript, cache = TRUE}
d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                     read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
  distinct()
```
